### 2015-07-08 narrative/qos.tex
temporarily removed "research questions" from QoS as they don't match the text.

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.  Specifically, we will address the following research questions:
\begin{tightItemize}
  \item Can we make any guarantees in a scalable decentralized system?; 
 \item  What quality of service metrics can be make guarantees on in a scalable
    way?;
  \item What kind of error rates will we have in our estimation and what error
    rates are acceptable?;
  \item How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;
  \item  How do we make the scheduler scalable with the size of the system?
\end{tightItemize}

>>>>

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.

%Specifically, we will address the following research questions:
%\begin{tightItemize}
%  \item Can we make any guarantees in a scalable decentralized system?; 
% \item  What quality of service metrics can be make guarantees on in a scalable
%    way?;
%  \item What kind of error rates will we have in our estimation and what error
%    rates are acceptable?;
%  \item How much will the qos scheduler, admission control, manager cost in
%    terms of resources and time?;
%  \item  How do we make the scheduler scalable with the size of the system?
%\end{tightItemize}
